Cluster Dynamics with HETDEX - I: Simulated Performance, Mass Distribution and Limits

### 2015-10-12 ms.tex
keep working

\subsection{The ``Buzzard'' Catalogs}
The ``Buzzard'' mock galaxy catalogs (R. Wechsler et al., private communication) are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.

@@

\subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec:oii luminosity}
\begin{figure*} 
	\includegraphics[width=\textwidth]{oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{2}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss} 
\end{figure*}

The buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically. We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.

@@

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{f01.pdf} 
	\caption{Representative observation tiling scheme for the HETDEX $16'$ pointings. Each colored square is a single VIRUS IFU and the dashed octagons approximate the size of a single observation. See the text for more details.} \label{fig:ifu layout} 
\end{figure}

In this work we consider two separate observation cases. The first are targeted observations where we select each galaxy cluster and ``observe'' each galaxy within $8'$ of the center. The second is a survey case where observations which are blind to the positions of the clusters are conducted. In both cases, our ``observations'' consist of placing masks down onto the buzzard ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath. Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig:ifu layout}. The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}. The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.

The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing. This means that when selecting galaxies from the buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig:ifu layout}. Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next.

@@

\acknowledgments 
The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work. This research made use of This research made use of \textsc{APLpy}, an open-source plotting package for Python hosted at http://aplpy.github.com; the \textsc{IPython} package \citep{Perez2007}; \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}. Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/. The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.

>>>>

\subsection{The ``Buzzard'' Catalogs}
The ``Buzzard'' mock galaxy catalogs (R. Wechsler et al., private communication) cover 375.68 \degsq\ between $60 < RA < 90$ and $-61 < DEC < -41$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.

@@

\subsection{ {\rm[\ion{O}{ii}]} Luminosity}\label{sec:oii luminosity}
\begin{figure*} 
	\includegraphics[width=\textwidth]{oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram.} \label{fig:oii sdss} 
\end{figure*}

The Buzzard ``truth'' catalog does not provide [\ion{O}{ii}] luminosities so we must assign them empirically. We use 503113 galaxies from the SDSS Data Release 12 \citep{Alam2015} from $z = 0.05 - 0.2$, which are selected with no redshift warning, and place each galaxy on a color-magnitude diagram (CMD) of $M_r$ and $g-r$, see Figure~\ref{fig:oii sdss}.

@@

\begin{figure} 
	\includegraphics[width=0.49\textwidth]{f01.pdf} 
	\caption{Representative observation tiling scheme for the HETDEX $16' \times 16'$ pointings. Each colored square is a single VIRUS IFU and the dashed octagons approximate the size of a single observation. See the text for more details.} \label{fig:ifu layout} 
\end{figure}

In this work we consider two separate observation cases. The first are targeted observations where we select each galaxy cluster and ``observe'' each galaxy within $8'$ of the center. The second is a survey case where observations which are blind to the positions of the clusters are conducted. In both cases, our ``observations'' consist of placing masks down onto the Buzzard ``truth'' catalogs and selecting all, $z< 0.5$ also meeting sensitivity limits, galaxies which lie underneath. Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig:ifu layout}. The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}. The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.

The individual IFUs have a fill-factor of 1/3, which will be completely filled with three dithers of the telescope at each pointing. This means that when selecting galaxies from the Buzzard catalog we assume an observation for all galaxies laying within a colored, IFU square in Figure~\ref{fig:ifu layout}. \editorial{This should be updated with the fiber collisions.} Galaxies which lie between the IFUs are missed, as well as the galaxies which lie between the pointings, as there is no overlap between one pointing and the next. To cover the 375.67 \degsq\ field of the Buzzard catalog we require 5370 pointings where 0.015 \degsq\ of each pointing is covered by an IFU. The total area of the sky covered by an IFU is 80.80 \degsq\ which gives a filling factor of 1/4.65 slight decreased from the expected filling factor of 1/4.5.

@@

\acknowledgments 
The authors also wish to thank the anonymous referee whose comments and suggestions significantly improved both the quality and clarity of this work. We also thank Steven W. Crawford for many helpful discussions. This research made use of This research made use of \textsc{APLpy}, an open-source plotting package for Python hosted at http://aplpy.github.com; the \textsc{IPython} package \citep{Perez2007}; \textsc{matplotlib}, a Python library for publication quality graphics \citep{Hunter2007}. Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, the U.S. Department of Energy, the National Aeronautics and Space Administration, the Japanese Monbukagakusho, the Max Planck Society, and the Higher Education Funding Council for England. The SDSS Web Site is http://www.sdss.org/. The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
